---
title: "Practical 12"
format: html
---

### Setup

```{r setup, warning=FALSE, message=FALSE}
library(foreach) # uses %do%
library(doParallel) # uses %dopar%
library(MASS) # glalaxies data for Q2
library(iterators) # for Question 4 (irnorm)
```

### Quetsion 1

```{r}
cl <- makeCluster(3)
registerDoParallel(cl)

exp_mean_and_var <- foreach(i = 1:1000, .combine = rbind) %dopar% {
    random_sample <- rexp(100,rate=1)
    sample_mean <- mean(random_sample)
    sample_variance <- var(random_sample)
    rbind(sample_mean,sample_variance)
    c(sample_mean, sample_variance)
}

stopCluster(cl)
```

```{r}
colnames(exp_mean_and_var) <- c("Mean", "Variance")
head(exp_mean_and_var)
```

### Question 2

```{r}
data <- galaxies
head(data)
```
Serial Processing:

```{r}
system.time({
  galaxies_bs_medians <- foreach(i = 1:1000, .combine = c) %do% {
    bs_sample <- sample(galaxies,length(galaxies),replace = T)
    bs_median <- median(bs_sample)
}
})
```


```{r}
hist(galaxies_bs_medians)
```

In parallel:

```{r}

```


```{r}
cl <- makeCluster(3)
registerDoParallel(cl)

system.time({
  galaxies_bs_medians <- foreach(i = 1:1000, .combine = c) %dopar% {
    bs_sample <- sample(data,length(data),replace = T)
    bs_median <- median(bs_sample)
}
})


stopCluster(cl)
```

The serial processing time was approximately equal to the parallel processing time.

Now we will try doing 1000 bootstrap samples at a time:

```{r}
cl <- makeCluster(3)
registerDoParallel(cl)

system.time({
  galaxies_bs_medians_1000 <- foreach(i = 1:3, .combine = c) %dopar% {
    bs_sample_1000 <- replicate(1000,median(sample(data,length(data),replace = T)))
    bs_sample_1000
}
})

stopCluster(cl)
```

```{r}
hist(galaxies_bs_medians_1000)
```
In this case, despite computing 3000 bootstrap medians, the processing time was much faster.

### Question 3

Coverage of a percentile bootstrap confidence interval for the median:

```{r}
cl <- makeCluster(3)
registerDoParallel(cl)

sample <- rexp(n = 50, rate = 1)
sample_mean <- mean(sample)
n <- 1000

system.time({
  coverage_pci_bs <- foreach(i = 1:n, .combine = c) %dopar% {
    new_sample <- rexp(n = 50, rate = 1/sample_mean)
    bs_sample_1000 <- replicate(n,mean(sample(new_sample,length(new_sample),replace = T)))
    mean_quantiles <- quantile(bs_sample_1000,probs = c(0.025,0.975))
  coverage_check <- if (mean_quantiles[1] <= sample_mean & sample_mean <= mean_quantiles[2]) {
  1
  } else {
    0
  }
  coverage_check
}
})

stopCluster(cl)
```
We now have the number of times our confidence interval contained the original sample mean out of 1000. Therefore, the coverage is as follows:

```{r}
coverage <- sum(coverage_pci_bs)/n
coverage
```
### Question 4

```{r}
set.seed(1234)

cl <- makeCluster(3)
registerDoParallel(cl)

vector_maxes <- foreach(i = 1:3, .combine = c, .packages = "iterators") %dopar% {
  vec <- irnorm(n = 5, mean = 0, sd = 1)
  # Pull all numbers into a numeric vector
  vec_numbers <- numeric(5)
  vec_numbers[1] <- nextElem(vec)
  vec_numbers[2] <- nextElem(vec)
  vec_numbers[3] <- nextElem(vec)
  vec_numbers[4] <- nextElem(vec)
  vec_numbers[5] <- nextElem(vec)
  max(vec_numbers)
}

stopCluster(cl)

vector_maxes
```


```{r}
set.seed(1234)  # set seed BEFORE foreach

# Use foreach and irnorm to generate 3 vectors of 5 random normals
largest_values <- foreach(i = 1:3, .combine = c) %do% {
  # create an iterator of 5 normal random numbers
  vec_iter <- irnorm(n = 5, mean = 0, sd = 1)
  
  # pull all 5 numbers from the iterator into a numeric vector
  vec <- sapply(1:5, function(x) nextElem(vec_iter))
  
  # find the largest value
  max(vec)
}

largest_values
```




### Question 5


tbc