---
title: "Practical 12"
format: html
---

### Setup

```{r setup, warning=FALSE, message=FALSE}
library(foreach) # uses %do%
library(doParallel) # uses %dopar%
library(MASS) # glalaxies data for Q2
library(iterators) # for Question 4 (irnorm)
library(tibble)
library(knitr)
```

### Quetsion 1

```{r}
cl <- makeCluster(3)
registerDoParallel(cl)

exp_mean_and_var <- foreach(i = 1:100, .combine = rbind) %dopar% {
    random_sample <- rexp(100,rate=1)
    sample_mean <- mean(random_sample)
    sample_variance <- var(random_sample)
    rbind(sample_mean,sample_variance)
    c(sample_mean, sample_variance)
}

stopCluster(cl)

colnames(exp_mean_and_var) <- c("Mean", "Variance")
```

Below are the first 10 rows of our resulting Mean and Variance for each of our 100 random samples:

```{r}
exp_mean_and_var_tb <- as_tibble(exp_mean_and_var)
exp_mean_and_var_tb
```

### Question 2

```{r}
data <- galaxies
head(data)
```
Serial Processing:

```{r}
system.time({
  galaxies_bs_medians <- foreach(i = 1:1000, .combine = c) %do% {
    bs_sample <- sample(galaxies,length(galaxies),replace = T)
    bs_median <- median(bs_sample)
}
})
```


```{r}
hist(galaxies_bs_medians)
```

In parallel:

```{r}

```


```{r}
cl <- makeCluster(3)
registerDoParallel(cl)

system.time({
  galaxies_bs_medians <- foreach(i = 1:1000, .combine = c) %dopar% {
    bs_sample <- sample(data,length(data),replace = T)
    bs_median <- median(bs_sample)
}
})


stopCluster(cl)
```

The serial processing time was approximately equal to the parallel processing time.

Now we will try doing 1000 bootstrap samples at a time:

```{r}
cl <- makeCluster(3)
registerDoParallel(cl)

system.time({
  galaxies_bs_medians_1000 <- foreach(i = 1:3, .combine = c) %dopar% {
    bs_sample_1000 <- replicate(
      1000,median(sample(data,length(data),replace = T)))
    bs_sample_1000
}
})

stopCluster(cl)
```

```{r}
hist(galaxies_bs_medians_1000)
```
In this case, despite computing 3000 bootstrap medians, the processing time was much faster.

### Question 3

Coverage of a percentile bootstrap confidence interval for the median:

```{r}
cl <- makeCluster(3)
registerDoParallel(cl)

sample <- rexp(n = 50, rate = 1)
sample_mean <- mean(sample)
n <- 1000

system.time({
  coverage_pci_bs <- foreach(i = 1:n, .combine = c) %dopar% {
    new_sample <- rexp(n = 50, rate = 1/sample_mean)
    bs_sample_1000 <- replicate(
      n,mean(sample(new_sample,length(new_sample),replace = T)))
    mean_quantiles <- quantile(bs_sample_1000,probs = c(0.025,0.975))
  coverage_check <- if (
    mean_quantiles[1] <= sample_mean & sample_mean <= mean_quantiles[2]) {1} 
  else {0}
  coverage_check
}
})

stopCluster(cl)
```
We now have the number of times our confidence interval contained the original sample mean out of 1000. Therefore, the coverage is as follows:

```{r}
coverage <- sum(coverage_pci_bs)/n
coverage
```
### Question 4

```{r}
cl <- makeCluster(3)
registerDoParallel(cl)

set.seed(1234)

max_values <- foreach(vec = irnorm(5, count = 3),
                          .combine = c) %dopar% {
  max(vec)
}
stopCluster(cl)
```
The below 3 values are the maximum of each of the 3 vectors of 5 random variables:

```{r}
max_values
```


### Question 5

```{r}
time_foreach <- system.time({
  set.seed(1234)
  cl <- makeCluster(3)
  registerDoParallel(cl)
  max_values_foreach <- foreach(vec = irnorm(5, count = 3),
                          .combine = c) %dopar% {
  max(vec)
}
})

stopCluster(cl)

max_values_foreach
time_foreach
```

```{r}
time_parLapply <- system.time({
  set.seed(1234)
  cl <- makeCluster(3)
  registerDoParallel(cl)
  
  max_vec_func <- function(i){
    vec <- rnorm(5)
    max(vec)
  }
  
  max_values_parLapply <- parLapply(cl = cl, 1:3, max_vec_func)
  max_values_parLapply <- unlist(max_values_parLapply)
})

stopCluster(cl)

max_values_parLapply
time_parLapply
```

```{r}
time_replicate <- system.time({
  set.seed(1234)
  max_values_replicate <- replicate(3,max(rnorm(5)))
})

max_values_replicate
time_replicate
```
The table below shows shows the time it took each of the three above methods to run:

```{r}
times <- rbind(time_foreach,time_parLapply,time_replicate)
kable(times[,1:3], caption = "Times Comparison of Three Methods")
```
From the table above, we can see that the foreach and parLapply functions have a similar run times, with no noticeable difference between them. Replicate, however, despite not running in parallel is much faster, practically instant. The time it takes to setup the clusters in foreach and parLapply make them slower for such a simple task. The benefit of parallelisation was not worth it.


```{r}
max_values_all <- rbind(max_values_foreach,
                        max_values_parLapply,
                        max_values_replicate)
```

Below we compare the maximum values of each vector that each method produced:

```{r}
kable(round(max_values_all,2), 
      caption = "Max Value Comparison of Three Methods")
```

From the table above, we can see that the use of irnorm in the foreach function resulted in the seed working correctly, as it matches the values achieved by replicate. Unfortunately, parLapply did not achieve the same values as each worker generates its own random numbers independently.